Is structure based drug design ready for selectivity optimization?

### 2018-12-14 manuscript.tex
12/14/18

\paragraph{Free Energy Calculations}
The FEP+ panel (Maestro release 2017-4) was used to generate perturbation maps. Neutral perturbations were run for 15ns per replica, using an NPT ensemble and water buffer size of 5\AA. A GCMC solvation protocol was used to sample buried water molecules in the binding pocket prior to the calculation, which discards any retained crystal waters.

@@

\section{Acknowledgments}
JDC and SKA acknowledge support from NIH grant R01 121505.
JDC acknowledges partial support from NIH grant P30 CA008748.

@@

>>>>

\paragraph{Free Energy Calculations}
The FEP+ panel (Maestro release 2017-4) was used to generate perturbation maps. FEP+ calculations were run using the FEP+ panel from Maestro release 2018-3, using the parameters from the version of OPLS3e that shipped with the 2018-3 release. Any missing ligand torsions were fit using the automated FFbuilder protocol~\citep{Abel:Acc.Chem.Res.:2017}. Custom charges were assigned using the OPLS3e forcefield using input geometries, according to the automated FEP+ workflow released in 2018-3. Neutral perturbations were run for 15ns per replica, using an NPT ensemble and water buffer size of 5\AA. The SPC water model was used. A GCMC solvation protocol was used to sample buried water molecules in the binding pocket prior to the calculation, which discards any retained crystal waters.

@@

\section{Acknowledgments}
JDC and SKA acknowledge support from NIH grant R01GM121505.
JDC acknowledges partial support from NIH grant P30CA008748.

@@

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure4.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-4}
{\bf Each replicate of the CDK2/CDK9 calculates yields a consistent RMSE and MUE} \\
Single target potencies and selectivities for CDK2/ERK2 from the Blake datasets (\emph{top}), and CDK2/CDK9 (\emph{bottom}) from the Shao datasets. The experimental values are shown on the X-axis and calculated values on the Y-axis. Each data point corresponds to a ligand for a given target. All values are shown in units of kcal/mol. The horizontal error bars show the assumed experimental uncertainty of 0.3 kcal/mol\citep{BROWN2009420}. To better highlight outliers that are unlikely due simply to forcefield errors, we presume the forcefield error ($\sigma_\mathrm{FF} \approx$ 0.9 kcal mol$^{-1}$~\cite{Harder:J.Chem.TheoryComput.:2016}) also behaves as a random error. We show the total estimated statistical and forcefield error ($\sqrt{\sigma_\mathrm{FF}^2 + \sigma_\mathrm{calc}^2}$) as vertical blue error bars. The black vertical error bars correspond to the statistical error ($\sigma_{calc}$). The black line indicates agreement between calculation and experiment, while the gray shaded region represent 1.36 kcal/mol (or 1 log unit) error. The MUE and RMSE are shown on each plot with bootstrapped 95$\%$ confidence intervals. ({\bf A}) Replcicate 1 ({\bf B}) Replcicate 2 ({\bf C}) Replcicate 3 
}
\end{fullwidth}
\end{figure}

\begin{figure}[h]
\begin{fullwidth}
\begin{centering}
\includegraphics[width=1.0\linewidth]{figures/supp_figure5.pdf}
% Need at least one blank line for centering to work.
\end{centering}
\caption{
\label{fig:sup-figure-5}
{\bf Each replicate of the CDK2/CDK9 calculates yields consistent errors and correlation coefficient} \\
({\bf A}) (\emph{left}) The joint posterior distribution of the prediction errors for CDK2 (X-axis) and CDK9 (Y-axis) from the Bayesian graphical model for replicate 1. (\emph{right}) The posterior marginal distribution of the correlation coefficient ($\rho$) is shown in gray for replcicate 1. The inserted box shows the mean and 95\% confidence interval for the correlation coefficient. ({\bf B}) and ({\bf C}) The same as above, but for replicates 2 and 3, respectively
}
\end{fullwidth}
\end{figure}
